### 2025-07-01 machine-learning.qmd
20250701 - citations

We use the `caret` package [@R-caret].
We use the `parallel` [@R-parallel] and `doParallel` [@R-doParallel] packages for parallel (faster) processing.

@@

To combine tree-boosting with mixed models, we use the `gpboost` package [@gpboost].

>>>>

We use the `caret` package [@R-caret].
We use the `doParallel` [@R-doParallel] package for parallel (faster) processing.

@@

To combine tree-boosting with mixed models, we use the `gpboost` package [@R-gpboost].
